\chapter*{Abstract}\addcontentsline{toc}{chapter}{Abstract}
The topic of this thesis is efficiency of analog-to-digital
converters (ADC) in nano-scale CMOS technology. With  downscaling of CMOS
technology it is  harder to design ADCs. The power supply is reduced due to reliability concerns and the output resistance of
transistors is reduced because of shorter channel lengths. Such
challenges makes it harder to design ADCs with conventional circuit
techniques and ADC architectures.

We investigate two separate paths towards higher efficiency
in nano-scale CMOS technologies: circuit implementation, and ADC architectures. 

The research into ADC architectures assumes that circuit
implementation challenges will be solved. It looks at how a sigma-delta modulator can
be used as a front-end to pipelined ADCs. A new class of sigma-delta
modulators, the switched-capacitor (SC) open-loop sigma-delta
modulator (OLSDM) is introduced. We introduce the SC modulo integrator
and the SC modulo resonator that facilitates implementation of
sigma-delta modulators that do not have feedback of the quantized
signal. Thus, high-latency converters such as pipelined ADCs can be
used as quantizers. Limitations of OLSDM, like operational amplifier (opamp) DC gain,  quantizer
linearity, and input signal amplitude are discussed in
detail. Behavioral simulations of OLSDMs confirm the theory. 


The research into circuit implementations investigate how the opamp can be
removed from SC circuits. Two techniques are
investigated: open-loop residue amplification and comparator-based
switched-capacitor circuits (CBSC). 

 We
present the design of a 7-bit 200MS/s 2mW pipelined ADC based on
switched open-loop residue amplifiers.  By turning off the open-loop
amplifiers when they are not needed the  power
dissipation is reduced by 23\%. 

Comparator-based switched-capacitor circuits (CBSC) are an alternative
to opamp based SC circuits. By replacing the opamp
with a comparator and current sources the same charge transfer is
achieved. 

We discuss design equations for CBSC, and how one can model CBSC in
MATLAB and SPICE.

We present an 8-bit 60MS/s 8.5mW pipelined ADC with 7.05-bit effective
number of bits (ENOB). At the time of writing
it was the first silicon
proven differential CBSC pipelined ADC. 


