\twocolumn
\chapter{JSSC papers used in ADC survey}


%\begin{description}
\begin{enumerate}
\renewcommand\labelenumi{[\theenumi]}


\item
D.~Janssen, ``Delta modulation in dvm design,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~7, no.~6, 1972.

\item
T.~Hornak and J.~Corcoran, ``A high precision component-tolerant a/d
  convertor,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~10, no.~6, 1975.

\item
J.~McCreary and P.~Gray, ``All-mos charge redistribution analog-to-digital
  conversion techniques. i,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~10,
  no.~6, 1975.

\item
R.~Suarez, P.~Gray, and D.~Hodges, ``All-mos charge-redistribution
  analog-to-digital conversion techniques. i i,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~10, no.~6, 1975.

\item
G.~Smarandoiu, K.~Fukahori, P.~Gray, and D.~Hodges, ``An all-mos
  analog-to-digital converter using a constant slope approach,'' \emph{{IEEE}
  J. Solid-State Circuits}, vol.~11, no.~3, 1976.

\item
G.~Landsburg, ``A charge-balancing monolithic a/d converter,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~12, no.~6, 1977.

\item
R.~van~de Plassche and R.~van Der~Grift, ``A five-digit analog-digital
  converter,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~12, no.~6, 1977.

\item
A.~Brokaw, ``A monolithic 10-bit a/d using i/sup 2/l and lwt thin-film
  resistors,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~13, no.~6, 1978.

\item
A.~Hamade', ``A single chip all-mos 8-bit a/d converter,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~13, no.~6, 1978.

\item
Y.~Suzuki, E.~Masuda, C.~Satoh, and T.~Iida, ``A new single-chip c/sup 2/mos
  a/d converter for microprocessor systems-p enta-phase integrating c/sup 2/mos
  a/d converter,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~13, no.~6, 1978.

\item
U.~Fiedler and D.~Seitzer, ``A high-speed 8 bit a/d converter based on a
  gray-code multiple folding c ircuit,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~14, no.~3, 1979.

\item
H.~Kessler and P.~Jiru, ``A single-chip a/d converter in pmos technology for
  digital voltmeter app lications,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~14, no.~3, 1979.

\item
A.~Dingwall, ``Monolithic expandable 6 bit 20 mhz cmos/sos a/d converter,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~14, no.~6, 1979.

\item
B.~Fotouhi and D.~Hodges, ``High-resolution a/d conversion in mos/lsi,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~14, no.~6, 1979.

\item
J.~Peterson, ``A monolithic video a/d converter,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~14, no.~6, 1979.

\item
R.~van~de Plassche and R.~van Der~Grift, ``A high-speed 7 bit a/d converter,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~14, no.~6, 1979.

\item
T.~Redfern, J.~Connolly, Jr., S.~Chin, and T.~Frederiksen, ``A monolithic
  charge-balancing successive approximation a/d technique,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~14, no.~6, 1979.

\item
C.-M. Kyung and C.-K. Kim, ``Pipeline analog-to-digital conversion with
  charge-coupled devices,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~15,
  no.~2, 1980.

\item
H.-U. Post and K.~Waldschmidt, ``A high-speed nmos a/d converter with a current
  source array,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~15, no.~3, 1980.

\item
P.~Saul, A.~Fairgrieve, and A.~Fryers, ``Monolithic components for 100 mhz data
  conversion [4-bit expandable a/d convertor],'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~15, no.~3, 1980.

\item
G.~Emmert, E.~Navratil, H.~Parzefall, and R.~Rydval, ``A versatile bipolar
  monolithic 6-bit a/d converter for 100 mhz sample fr equency,'' \emph{{IEEE}
  J. Solid-State Circuits}, vol.~15, no.~6, 1980.

\item
M.~Timko and P.~Holloway, ``Circuit techniques for achieving high speed-high
  resolution a/d conversi on,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~15,
  no.~6, 1980.

\item
H.~Fiedler, B.~Hoefflinger, W.~Demmer, and P.~Draheim, ``A 5-bit building block
  for 20 mhz a/d converters,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~16,
  no.~3, 1981.

\item
P.~Saul, ``Successive approximation analog-to-digital conversion at video
  rates,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~16, no.~3, 1981.

\item
T.~Misawa, J.~Iwersen, L.~Loporcaro, and J.~Ruch, ``Single-chip per channel
  codec with filters utilizing /spl delta/-/spl si gma/ modulation,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~16, no.~4, 1981.

\item
C.~M. Kyung and C.~K. Kim, ``Charge-coupled analog-to-digital converter,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~16, no.~6, 1981.

\item
J.~Candy and B.~Wooley, ``Precise biasing of analog-to-digital converters by
  means of auto-zero fe edback,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~17, no.~6, 1982.

\item
R.~van~de Plassche and H.~Schouwenaars, ``A monolithic 14 bit a/d converter,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~17, no.~6, 1982.

\item
T.~Takemoto, M.~Inoue, H.~Sadamatsu, A.~Matsuzawa, and K.~Tsuji, ``A fully
  parallel 10-bit a/d converter with video speed,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~17, no.~6, 1982.

\item
H.~Bruggemann, ``Ultrafast feedback a/d conversion made possible by a
  nonuniform error qu antizer,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~18, no.~1, 1983.

\item
T.~Sugawara, M.~Ishibe, H.~Yamada, S.-I. Majima, T.~Tanji, and S.~Komatsu, ``A
  monolithic 14 bit/20 /spl mu/s dual channel a/d converter,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~18, no.~6, 1983.

\item
R.~V.~D. Grift and R.~van~de Plassche, ``A monolithic 8-bit video a/d
  converter,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~19, no.~3, 1984.

\item
A.~Silburt, A.~Boothroyd, and M.~Elmasry, ``A novel multiple threshold mosfet
  structure for a/d and d/a conversion,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~19, no.~5, 1984.

\item
J.~Doernberg, H.-S. Lee, and D.~Hodges, ``Full-speed testing of a/d
  converters,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~19, no.~6, 1984.

\item
H.~Fiedler and B.~Hoefflinger, ``A cmos pulse density modulator for
  high-resolution a/d converters,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~19, no.~6, 1984.

\item
M.~Inoue, H.~Sadamatsu, A.~Matsuzawa, A.~Kanda, and T.~Takemoto, ``A monolithic
  8-bit a/d converter with 120 mhz conversion rate,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~19, no.~6, 1984.

\item
H.-S. Lee, D.~Hodges, and P.~Gray, ``A self-calibrating 15 bit cmos a/d
  converter,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~19, no.~6, 1984.

\item
P.~Li, M.~Chin, P.~Gray, and R.~Castello, ``A ratio-independent algorithmic
  analog-to-digital conversion technique,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~19, no.~6, 1984.

\item
Y.~Yoshii, K.~Asano, M.~Nakamura, and C.~Yamada, ``An 8 bit, 100 ms/s flash
  adc,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~19, no.~6, 1984.

\item
A.~Yukawa, ``A cmos 8-bit high-speed a/d converter ic,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~20, no.~3, 1985.

\item
B.~Zojer, R.~Petschacher, and W.~Luschnig, ``A 6-bit/200-mhz full nyquist a/d
  converter,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~20, no.~3, 1985.

\item
A.~Dingwall and V.~Zazzu, ``An 8-mhz cmos subranging 8-bit a/d converter,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~20, no.~6, 1985.

\item
M.~Hotta, K.~Maio, N.~Yokozawa, T.~Watanabe, and S.~Ueda, ``A 150-mw, 8-bit
  video-frequency a/d converter,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~21, no.~2, 1986.

\item
T.~Ducourant, J.-C. Baelde, M.~Binet, and C.~Rocher, ``1-ghz, 16-mw, 2-bit
  analog-to-digital gaas converter,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~21, no.~3, 1986.

\item
A.~Joy, R.~Killips, and P.~Saul, ``An inherently monotonic 7-bit cmos adc for
  video applications,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~21, no.~3,
  1986.

\item
U.~Roettcher, H.~Fiedler, and G.~Zimmer, ``A compatible cmos-jfet pulse density
  modulator for interpolative high-re solution a/d conversion,'' \emph{{IEEE}
  J. Solid-State Circuits}, vol.~21, no.~3, 1986.

\item
C.~Shih and P.~Gray, ``Reference refreshing cyclic analog-to-digital and
  digital-to-analog conv erters,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~21, no.~4, 1986.

\item
K.~Bacrania, ``A 12-bit successive-approximation-type adc with digital error
  correction,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~21, no.~6, 1986.

\item
R.~Koch, B.~Heise, F.~Eckbauer, E.~Engelhardt, J.~Fisher, and F.~P. all, ``A
  12-bit sigma-delta analog-to-digital converter with a 15-mhz clock rat e,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~21, no.~6, 1986.

\item
T.~Kumamoto, M.~Nakaya, H.~Honda, S.~Asai, Y.~Akasaka, and Y.~Horiba, ``An
  8-bit high-speed cmos a/d converter,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~21, no.~6, 1986.

\item
B.~Peetz, B.~Hamilton, and J.~Kang, ``An 8-bit 250 megasample per second
  analog-to-digital converter: operatio n without a sample and hold,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~21, no.~6, 1986.

\item
P.~Yee, ``Noise considerations in high-accuracy a/d converters,'' \emph{{IEEE}
  J. Solid-State Circuits}, vol.~21, no.~6, 1986.

\item
P.~Grant and K.~Smith, ``Monotonic dual-ladder a/d conversion,'' \emph{{IEEE}
  J. Solid-State Circuits}, vol.~22, no.~2, 1987.

\item
J.~Robert, G.~Temes, V.~Valencic, R.~Dessoulavy, and P.~Deval, ``A 16-bit
  low-voltage cmos a/d converter,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~22, no.~2, 1987.

\item
R.~van~de Grift, I.~Rutten, and M.~V.~D. Veen, ``An 8-bit video adc
  incorporating folding and interpolation techniques,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~22, no.~6, 1987.

\item
M.~Hotta, T.~Shimizu, K.~Maio, K.~Nakazato, and S.~Ueda, ``A 12-mw 6-bit
  video-frequency a/d converter,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~22, no.~6, 1987.

\item
S.~Lewis and P.~Gray, ``A pipelined 5-msample/s 9-bit analog-to-digital
  converter,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~22, no.~6, 1987.

\item
Y.~Matsuya, K.~Uchimura, A.~Iwata, T.~Kobayashi, M.~Ishikawa, and T.~Y. itome,
  ``A 16-bit oversampling a-to-d conversion technology using triple-integrat
  ion noise shaping,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~22, no.~6,
  1987.

\item
K.~Poulton, J.~Corcoran, and T.~Hornak, ``A 1-ghz 6-bit adc system,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~22, no.~6, 1987.

\item
T.~KUMAMOTO, M.~NAKAYA, MEMBER, S.~KUSUNOKI, T.~NISHIMURA, N.~YAZAWA,
  Y.~AKASAKA, , and Y.~HORIBA, ``An soi structure for flash a/d converter,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~23, no.~1, 1988.

\item
H.~Onodera, T.~Tateishi, and K.~Tamaru, ``A cyclic a/d converter that does not
  require ratio-matched components,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~23, no.~1, 1988.

\item
D.~DANIEL, U.~LANGMANN, and B.~G. BOSCH, ``A silicon bipolar 4-bit 1-gsample/s
  full nyquist a/d converter,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~23,
  no.~3, 1988.

\item
J.~ROBERT and P.~DEVAL, ``A second-order high-resolution incremental a/d
  converter with offset and charge injection compensation,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~23, no.~3, 1988.

\item
B.-S. Song, ``A 12-bit l-msample/s capacitor error -averaging pipelined a/d
  converter,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~23, no.~6, 1988.

\item
Fernandes, ``A 14-bit 10- mu s subranging a/d converter with s/h,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~23, no.~6, 1988.

\item
Plassche, ``An 8-bit 100-mhz full-nyquist analog-to-digital converter,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~23, no.~6, 1988.

\item
Sutarja, ``A pipelined 13-bit 250-ks/s 5-v analog-to-digital converter,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~23, no.~6, 1988.

\item
T.~Wakimoto, Y.~Akazawa, and S.~Konaka, ``Si bipolar 2-ghz 6-bit flash a/d
  conversion lsi - solid-state circuits, ieee journal of,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~23, no.~6, 1988.

\item
T.~SHIMIZU, M.~HOTTA, K.~MAIO, , and S.~UEDA, ``A 10-bit 20-mhz two-step
  parallel a/d converter with internal s/h,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~24, no.~1, 1989.

\item
J.~Doernberg, P.~R. Gray, and D.~A. Hodges, ``A 10-bit 5-msample/s cmos
  two-step flash adc - solid-state circuits, ieee journal of,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~24, no.~2, 1989.

\item
V.~E. GARUTS, Y.-C.~S. YU, MEMBER, IEEE, E.~0.TRAA, , and T.~YAMAGUCHI, ``A
  dual 4-bit 2-gs/s full nyquist analog-to-digital converter using a 70-ps
  silicon bipolar technolog,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~24,
  no.~2, 1989.

\item
Kerth, ``A 12-bit, 1-mhz, two-step flash adc,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~24, no.~2, 1989.

\item
Norsworthy, ``A 14-bit 80-khz sigma-delta a/d converter: modeling, design and
  performance evaluation,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~24,
  no.~2, 1989.

\item
F.~THOMAS, F.~DEBRIE, M.~GLOANEC, MEMBER, M.~L. PAIH, P.~MARTIN, T.~NGUYEN,
  S.~RUGGERI, , and J.-M. URO, ``1-ghz gaas adc building blocks,'' \emph{{IEEE}
  J. Solid-State Circuits}, vol.~24, no.~2, 1989.

\item
A.~K. JOY, MEMBER, IEEE, A.~J. HOLDEN, T.~C. LESLIE, MEMBER, IEEE, , and P.~H.
  SAUL, ``A comparison of gaas hjbt and silicon bipolar technologies for
  high-speed analog-to-digital converters,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~24, no.~3, 1989.

\item
Rodgers, ``A monolithic 5 1/2-digit bimos a/d converter,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~24, no.~3, 1989.

\item
Y.~Sugimoto and S.~Mizoguchi, ``An experimental bicmos video 10 bit adc -
  solid-state circuits, ieee journal of,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~24, no.~4, 1989.

\item
M.~ISHIKAWA, MEMBER, IEEE., and T.~TSUKAHARA, ``An 8-bit 50-mhz cmos subranging
  a/d converter with pipelined wide-band s/h,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~24, no.~6, 1989.

\item
Kolluri, ``A 12-bit 500-ns subranging adc,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~24, no.~6, 1989.

\item
M.~K. MAYES and S.~W. CHIN, ``A multistep a/d converter family with efficient
  architecture,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~24, no.~6, 1989.

\item
R.~K. HESTER, S.~MEMBER, K.-S. TAN, MEMBER, M.~D. WIT, MEMBER, J.~w.~FAmARUSO,
  MEMBER, SAM1KIRIAKI, MEMBER, , J.~R. HELLUMS, and MEMBER, ``Fully
  differential adc with rail-to-rail common-mode range and nonlinear capacitor
  compensation,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~25, no.~1, 1990.

\item
S.~Hosotani, T.~Miki, A.~Maeda, and N.~Yazawa, ``An 8-bit 20-ms/s cmos a/d
  converter with 50-mw power consumption,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~25, no.~1, 1990.

\item
Mangelsdorf, ``A 400-mhz input flash converter with error correction,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~25, no.~1, 1990.

\item
G.~C. TEMES, F.~K. HADIDI, V.~s.TSO, MEMBER, and AND, ``An 8-b 1.3-mhz
  successive-approximation a/d converter,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~25, no.~3, 1990.

\item
D.~G. Nairn and C.~A.~T. Salama, ``Current-mode algorithmic analog-to-digital
  converters - solid-state circuits, ieee journal of,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~25, no.~4, 1990.

\item
R.~PETSCHACHER, MEMBER, IEEE, B.~ZOJER, B.~ASTEGHER, H.~JESSNER, , and
  A.~LECHNER, ``A 10-b 75-msps subranging a/d converter with integrated sample
  and hold,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~25, no.~6, 1990.

\item
B.~P.~D. Signore, D.~A. Kerth, N.~S. Sooch, and E.~J. Swanson, ``A monolithic
  2-b delta-sigma a/d converter - solid-state circuits, ieee journal of,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~25, no.~6, 1990.

\item
Song, ``A 10-b 15-mhz cmos recycling two-step a/d converter,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~25, no.~6, 1990.

\item
B.~P. Brandt and B.~A. Wooley, ``A 50-mhz multibit sigma-delta modulator for
  12-b 2-mhz a/d conversion - solid-state circuits, ieee journal of,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~26, no.~12, 1991.

\item
R.~G. Lerch, M.~H. Lamkemeyer, H.~L. Fiedler, W.~Bradinal, and P.~Becker, ``A
  monolithic sigma-delta a/d and d/a converter with filter for broad-band
  speech coding,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~26, no.~12,
  1991.

\item
D.~A. Mercer, ``A 12-b 750-ns subranging a/d converter with self-correcting
  s/h,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~26, no.~12, 1991.

\item
D.~B. Ribner, R.~D. Baertsch, S.~L. Garverick, D.~T. McGrath, J.~E. Krisciunas,
  , and T.~Fujii, ``A third-order multistage sigma-delta modulator with reduced
  sensitivity to nonidealities,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~26, no.~12, 1991.

\item
C.~Schiller and P.~Byrne, ``A 4-ghz 8-b adc system - solid-state circuits, ieee
  journal of,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~26, no.~12, 1991.

\item
V.~Comino, M.~S.~J. Steyaert, and G.~C. Temes, ``A first-order current-steering
  sigma-delta modulator,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~26,
  no.~3, 1991.

\item
B.~P. Brandt, D.~E. Wingard, , and B.~A. Wooley, ``Second-order sigma-delta
  modulation for digital-audio signal acquisition,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~26, no.~4, 1991.

\item
Y.-M. Lin, B.~Kim, and P.~R.Gray, ``A 13-b 2.5-mhz self-calibrated pipelined
  a/d converter in 3- mu m cmos,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~26, no.~4, 1991.

\item
H.~A. Leopold, G.~Winkler, P.~O’Leary, K.~Ilzer, and J.~Jernej, ``A
  monolithic cmos 20-b analog-to-digital converter,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~26, no.~7, 1991.

\item
P.~J.~A. Naus and E.~C. Dijkmans, ``Multibit oversampled sigma-delta a/d
  converters as front end for cd players,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~26, no.~7, 1991.

\item
P.~Real, D.~H. Robertson, C.~W. Mangelsdorf, Member, and T.~L. Tewksbury, ``A
  wide-band 10-b 20 ms/s pipelined adc using current-mode signals,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~26, no.~8, 1991.

\item
Y.~Nejime, M.~Hotta, and S.~Ueda, ``An 8-b adc with over-nyquist input at
  300-ms/s conversion rate,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~26,
  no.~9, 1991.

\item
R.~Hagelauer, ZEEE, F.~Oehler, G.~Rohmer, J.~Sauerer, , and D.~Seitzer, ``A
  gigasample/second 5-b adc with on-chip track and hold based on an industrial
  1 mu m gaas mesfet e/d process,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~27, no.~10, 1992.

\item
S.-H. Lee and B.-S. Song, ``Digital-domain calibration of multistep
  analog-to-digital converters,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~27, no.~12, 1992.

\item
B.~Razavi and B.~A. Wooley, ``A 12-b 5-msample/s two-step cmos a/d converter,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~27, no.~12, 1992.

\item
J.~van Valburg and R.~J. van~de Plassche, ``An 8-b 650-mhz folding adc,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~27, no.~12, 1992.

\item
S.~H. Lewis, H.~S. Fetterman, G.~F. Gross, Jr., R.~Ramachandran, and T.~R.
  Viswanathan, ``A 10-b 20-msample/s analog-to-digital converter,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~27, no.~3, 1992.

\item
L.~L. Toumelin, P.~Carbou, Y.~Leduc, P.~Guignon, J.~Oredsson, and A.~Lindberg,
  ``A 5-v cmos line controller with 16-b audio converters,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~27, no.~3, 1992.

\item
S.~J. Daubert and D.~Vallancourt, ``A transistor-only current-mode sigma-delta
  modulator - solid-state circuits, ieee journal of,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~27, no.~5, 1992.

\item
B.~Ginetti, P.~G.~A. Jespers, and A.~Vandemeulebroecke, ``A cmos 13-b cyclic
  rsd a/d converter - solid-state circuits, ieee journal of,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~27, no.~7, 1992.

\item
W.~T. Colleran and A.~A. Abidi, ``A 10-b, 75-mhz two-stage pipelined bipolar
  a/d converter - solid-state circuits, ieee journal of,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~28, no.~12, 1993.

\item
J.~W. Fattaruso, S.~Kiriaki, M.~de~Wit, and G.~Warwar, ``Self-calibration
  techniques for a second-order multibit sigma-delta modulator,'' \emph{{IEEE}
  J. Solid-State Circuits}, vol.~28, no.~12, 1993.

\item
A.~N. Karanicolas, IEEE, H.-S. Lee, IEEE, K.~L. Bacrania, and IEEE, ``A 15-b
  1-msample/s digitally self-calibrated pipeline adc,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~28, no.~12, 1993.

\item
K.~Kusumoto, A.~Matsuzawa, and K.~Murata, ``A 10-b 20-mhz 30-mw pipelined
  interpolating cmos adc,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~28,
  no.~12, 1993.

\item
K.~Sone, Y.~Nishida, and N.~Nakadai, ``A 10-b 100-msample/s pipelined
  subranging bicmos adc,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~28,
  no.~12, 1993.

\item
S.~A. Jantzi, W.~M. Snelgrove, P.~F. Ferguson, and Jr., ``A fourth-order
  bandpass sigma-delta modulator,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~28, no.~3, 1993.

\item
M.~Yotsuyanagi, T.~Etoh, and K.~Hirata, ``A 10 b 50 mhz pipelined cmos a/d
  converter with s/h - solid-state circuits, ieee journal of,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~28, no.~3, 1993.

\item
C.~S.~G. Conroy, D.~W. Cline, P.~R. Gray, and IEEE, ``An 8-b 85-ms/s parallel
  pipeline a/d converter in 1- mu m cmos,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~28, no.~4, 1993.

\item
H.~Kimura, A.~Matsuzawa, T.~Nakamura, and S.~Sawada, ``A 10-b 300-mhz
  interpolated-parallel a/d converter,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~28, no.~4, 1993.

\item
M.~de~Wit, K.-S. Tan, and R.~K. Hester, ``A low-power 12-b analog-to-digital
  converter with on-chip precision trimming - solid-state circuits, ieee
  journal of,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~28, no.~4, 1993.

\item
P.~J. Hurst, R.~A. Levinson, and D.~J. Block, ``A switched-capacitor
  delta-sigma modulator with reduced sensitivity to op-amp gain,'' \emph{{IEEE}
  J. Solid-State Circuits}, vol.~28, no.~6, 1993.

\item
S.-J. Wei, H.~C. Lin, R.~C. Potter, and D.~Shupe, ``A self-latching a/d
  converter using resonant tunneling diodes,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~28, no.~6, 1993.

\item
G.~Yin, F.~Stubbe, and W.~Sansen, ``A 16-b 320-khz cmos a/d converter using
  two-stage third-order sigma-delta noise shaping,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~28, no.~6, 1993.

\item
O.~J. A.~P. Nys and E.~Dijkstra, ``On configurable oversampled a/d
  converters,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~28, no.~7, 1993.

\item
T.~Okamoto, Y.~Maruyama, and A.~Yukawa, ``A stable high-order delta-sigma
  modulator with an fir spectrum distributor - solid-state circuits, ieee
  journal of,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~28, no.~7, 1993.

\item
M.~Ito, T.~Miki, S.~Hosotani, T.~Kumamoto, Y.~Yamashita, M.~Kijima, and T.~O.
  and, ``A 10 bit 20 ms/s 3 v supply cmos a/d converter,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~29, no.~12, 1994.

\item
Y.~Matsuya and J.~Yamada, ``1 v power supply, low-power consumption a/d
  conversion technique with swing-suppression noise shaping,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~29, no.~12, 1994.

\item
T.~Ritoniemi, E.~P.~S. Ingalsuo, T.~Husu, V.~Eerola, and T.~Saramiiki, ``A
  stereo audio sigma-delta a/d-converter,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~29, no.~12, 1994.

\item
G.~T. Uehara and P.~R. Gray, ``A 100 mhz a/d interface for prml magnetic disk
  read channels,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~29, no.~12,
  1994.

\item
L.~A. Williams, 111, and B.~A. Wooley, ``A third-order sigma-delta modulator
  with extended dynamic range,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~29, no.~3, 1994.

\item
H.-S. Lee, ``A 12-b 600 ks/s digitally self-calibrated pipelined algorithmic
  adc,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~29, no.~4, 1994.

\item
T.~Miki, H.~Kouno, T.~Kumamoto, Y.~Kinoshita, T.~Igarashi, and K.~Okada, ``A
  10-b 50 ms/s 500-mw a/d converter using a differential-voltage
  subconverter,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~29, no.~4, 1994.

\item
G.~Yin and W.~S. and, ``A high-frequency and high-resolution fourth-order /spl
  sigma//spl delta/ a/d converter in bicmos technology,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~29, no.~8, 1994.

\item
D.~Macq and P.~G.~A. Jespers, ``A 10-bit pipelined switched-current a/d
  converter,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~29, no.~8, 1994.

\item
M.~J.~M. Pelgrom, A.~C.~J. v.~Rens, M.~Vertregt, , and Marcel, ``A 25-ms/s
  8-bit cmos a/d converter for embedded application,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~29, no.~8, 1994.

\item
H.~Reyhani and P.~Quinlan, ``A 5 v, 6-b, 80 ms/s bicmos flash adcf,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~29, no.~8, 1994.

\item
J.~Yuan and C.~Svensson, ``A 10-bit 5-ms/s successive approximation adc cell
  used in a 70-ms/s adc array in 1.2-um cmos,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~29, no.~8, 1994.

\item
S.~Nadeem, C.~G. Sodini, and H.-S. Lee, ``16-channel oversampled
  analog-to-digital converter,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~29, no.~9, 1994.

\item
J.~F. Jensen, G.~Raghavan, A.~E. Cosand, and R.~H. Walden, ``A 3.2-ghz
  second-order delta-sigma modulator implemented in inp hbt technology -
  solid-state circuits, ieee journal of,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~30, no.~10, 1995.

\item
K.~Poulton, K.~L. Knudsen, A.~Member, J.~J. Corcoran, K.-C. Wann, R.~B.
  Nubling, R.~L. Pierson, M.-C.~F. Chang, and P.~M.~A. and, ``A 6-b, 4 gsa/s
  gaas hbt adc,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~30, no.~10, 1995.

\item
B.-S. Song, ``A fourth-order bandpass delta-sigma modulator with reduced number
  of op amps - solid-state circuits, ieee journal of,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~30, no.~12, 1995.

\item
B.~Nauta and G.~W. Venes, ``A 70-ms/s 110-mw 8-b cmos folding and interpolating
  a/d converter,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~30, no.~12, pp.
  1302--1308, 1995.

\item
M.~Yotsuyanagi, H.~Hasegawa, M.~Yamaguchi, M.~Ishida, and K.~Sone, ``A 2 v, 10
  b, 20 msample/s, mixed-mode subranging cmos a/d converter [special issue
  brief papers] - solid-state circuits, ieee journal of,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~30, no.~12, 1995.

\item
T.~B. Cho and P.~R. Gray, ``A 10 b, 20 msample/s, 35 mw pipeline a/d
  converter,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~30, no.~3, 1995.

\item
K.~Nakamura, M.~Hotta, L.~R. Carley, and D.~J. Allstot, ``An 85 mw, 10 b, 40
  msample/s cmos parallel-pipelined adc,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~30, no.~3, 1995.

\item
F.~W. Singor and W.~M. Snelgrove, ``Switched-capacitor bandpass delta-sigma a/d
  modulation at 10.7 mhz,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~30,
  no.~3, 1995.

\item
F.~Chen and B.~H. Leung, ``A high resolution multibit sigma-delta modulator
  with individual level averaging,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~30, no.~4, 1995.

\item
T.-H. Shu, B.-S. Song, and K.~Bacrania, ``A 13-b 10-msample/s adc digitally
  calibrated with oversampling delta-sigma converter,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~30, no.~4, 1995.

\item
C.-Y. Wu, C.-C. Chen, and J.-J. Cho, ``A cmos transistor-only 8-b 4.5-ms/s
  pipelined analog-to-digital converter using fully-differential current-mode
  circuit techniques,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~30, no.~5,
  1995.

\item
N.~Tan and S.~Eriksson, ``A low-voltage switched-current delta-sigma
  modulator,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~30, no.~5, 1995.

\item
W.-C. Song, H.-W. Choi, S.-U. Kwak, , B.-S. Song, SeniorMember, and ZEEE, ``A
  10-b 20-msample/s low-power cmos adc,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~30, no.~5, 1995.

\item
J.~Nedved, J.~Vanneuville, D.~Gevaert, and J.~Sevenhans, ``A transistor-only
  switched current sigma-delta a/d converter for a cmos speech codec,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~30, no.~7, 1995.

\item
D.~Kim, J.~Park, S.~Kim, D.-K. Jeong, and W.~Kim, ``A single chip /spl
  delta/-/spl sigma/ adc with a built-in variable gain stage and dac with a
  charge integrating subconverter for a 5 v 9600-bh modem,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~30, no.~8, 1995.

\item
D.~A. Mercer, ``A 14-b 2.5 msps pipelined adc with on-chip eprom,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~31, no.~1, 1996.

\item
T.-H. Shu, K.~Bacrania, and R.~Gokhale, ``A 10-b 40-msample/s bicmos a/d
  converter,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~31, no.~10, 1996.

\item
S.~Tsukamoto, I.~Dedic, T.~Endo, K.~yoshi Kikuta, K.~Goto, and O.~Kobayashi,
  ``A cmos 6-b, 200 msample/s, 3 v-supply a/d converter for a prml read chan
  nel lsi,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~31, no.~11, 1996.

\item
J.-E. Eklund and R.~Arvidsson, ``A multiple sampling, single a/d conversion
  technique for i/q demodulation in cmos,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~31, no.~12, 1996.

\item
G.-C. Ahn, H.-C. Choi, S.-I. Lim, S.-H. Lee, and C.-D. Lee, ``A 12-b, 10-mhz,
  250-mw cmos a/d converter,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~31,
  no.~12, 1996.

\item
M.~K. Mayes and S.~W. Chin, ``A 200 mw, 1 msample/s, 16-b pipelined a/d
  converter with on-chip 32-b microcontroller,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~31, no.~12, 1996.

\item
O.~Norman, ``A band-pass delta-sigma modulator for ultrasound imaging at 160
  mhz clock rate,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~31, no.~12,
  1996.

\item
S.~A. Paul and H.-S. Lee, ``A 9-b charge-to-digital converter for integrated
  image sensors,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~31, no.~12,
  1996.

\item
E.~J. van~der Zwan and E.~C. Dijkmans, ``A 0.2-mw cmos /spl sigma//spl delta/
  modulator for speech coding with 80 db dynamic range - solid-state circuits,
  ieee journal of,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~31, no.~12,
  1996.

\item
A.~G.~W. Venes and R.~J. van~de Plassche, ``An 80-mhz, 80-mw, 8-b cmos folding
  a/d converter with distributed track-and-hold preprocessing,'' \emph{{IEEE}
  J. Solid-State Circuits}, vol.~31, no.~12, 1996.

\item
P.~C. Yu and H.-S. Lee, ``A 2.5-v, 12-b, 5-msample/s pipelined cmos adc,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~31, no.~12, 1996.

\item
M.~K. Mayes, S.~W. Chin, and L.~L. Stoian, ``A low-power 1 mhz, 25 mw 12-bit
  time-interleaved analog-to-digital converter,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~31, no.~2, 1996.

\item
R.~T. Baird and T.~S.~. Fiez, ``A low oversampling ratio 14-b 500-khz /spl
  delta/spl sigma/ adc with a self-calibrated multibit dac,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~31, no.~3, 1996.

\item
T.~V. Burmas, K.~C. Dyer, P.~J. Hurst, and S.~H. Lewis, ``A second-order
  double-sampled delta-sigma modulator using additive-error switching,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~31, no.~3, 1996.

\item
D.~W.~C. and, ``A power optimized 13-b 5 msamples/s pipelined analog-to-digital
  converter in 1.2 /spl mu/m cmos,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~31, no.~3, 1996.

\item
M.~Bracey, W.~Redman-White, J.~Richardson, and J.~B. Hughes, ``A full nyquist
  15 ms/s 8-b differential switched-current a/d converter,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~31, no.~7, 1996.

\item
R.~Roovers and M.~S.~J. Steyaert, ``A 175 ms/s, 6 b, 160 mw, 3.3 v cmos a/d
  converter,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~31, no.~7, 1996.

\item
C.~L. Portmann, ZEEE, and T.~H.~Y. Meng, ``Power-efficient metastability error
  reduction in cmos flash a/d converters,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~31, no.~8, 1996.

\item
M.~P. Flynn and D.~J. Allstot, ``Cmos folding a/d converters with current-mode
  interpolation,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~31, no.~9, 1996.

\item
M.~Hqivin, A.~Olsen, T.~S. Lande, and C.~Toumazou, ``Delta-sigma modulators
  using frequency-modulated intermediate values,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~32, no.~1, 1997.

\item
T.~L. Brooks, D.~H. Robertson, D.~F. Kelly, A.~D. Muro, and S.~W. Harston, ``A
  cascaded sigma–delta pipeline a/d converter with 1.25 mhz signal bandwidth
  and 89 db snr,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~32, no.~12,
  1997.

\item
K.~Bult and A.~Buchwald, ``An embedded 240-mw 10-b 50-ms/s cmos adc in 1-mm/sup
  2/,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~32, no.~12, 1997.

\item
S.~Jantzi, K.~Martin, and A.~Sedra, ``Quadrature bandpass ΔΣ modulation for
  digital radio,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~32, no.~12,
  1997.

\item
S.-U. Kwak, B.-S. Song, and K.~Bacrania, ``A 15-b, 5-msample/s low-spurious
  cmos adc,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~32, no.~12, 1997.

\item
A.~Ong and B.~Wooley, ``A two-path bandpass ΣΔ modulator for digital if
  extraction at 20 mhz,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~32,
  no.~12, 1997.

\item
D.~Senderowicz, G.~Nicollini, S.~Pernici, A.~Nagari, P.~Confalonieri, and
  C.~Dallavalle, ``Low-voltage double-sampled ΣΔ converters,'' \emph{{IEEE}
  J. Solid-State Circuits}, vol.~32, no.~12, 1997.

\item
P.~Vorenkamp and R.~Roovers, ``A 12-b, 60-msample/s cascaded folding and
  interpolating adc,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~32, no.~12,
  1997.

\item
S.~Au and B.~H. Leung, ``A 1.95-v, 0.34-mw, 12-b sigma-delta modulator
  stabilized by local feedba ck loops,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~32, no.~3, 1997.

\item
I.~Fujimori, K.~Koyama, D.~Trager, F.~Tam, and L.~Longo, ``A 5-v single-chip
  delta-sigma audio a/d converter with 111 db dynamic ra nge,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~32, no.~3, 1997.

\item
K.~Y. Kim, N.~Kusayanagi, and A.~A. Abidi, ``A 10-b, 100-ms/s cmos a/d
  converter,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~32, no.~3, 1997.

\item
K.~Nagaraj, H.~S. Fetterman, J.~Anidjar, S.~H. Lewis, and R.~G. Renninger, ``A
  250-mw, 8-b, 52-msamples/s parallel-pipelined a/d converter with reduc ed
  number of amplifiers,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~32,
  no.~3, 1997.

\item
F.~Chen and B.~Leung, ``A 0.25-mw low-pass passive sigma-delta modulator with
  built-in mixer for a 10-mhz if input,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~32, no.~6, 1997.

\item
S.~Rabii and B.~A. Wooley, ``A 1.8-v digital-audio sigma-delta modulator in
  0.8-/spl mu/m cmos,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~32, no.~6,
  1997.

\item
D.~McCartney, A.~Sherry, J.~O’Dowd, and P.~Hickey, ``A low-noise low-drift
  transducer adc,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~32, no.~7,
  1997.

\item
N.~Moeneclaey and A.~Kaiser, ``Design techniques for high-resolution
  current-mode sigma-delta modulator s,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~32, no.~7, 1997.

\item
O.~Nys and R.~K. Henderson, ``A 19-bit low-power multibit sigma-delta adc based
  on data weighted avera ging,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~32, no.~7, 1997.

\item
V.~Peluso, M.~S.~J. Steyaert, and W.~Sansen, ``A 1.5-v-100-/spl mu/w /spl
  delta//spl sigma/ modulator with 12-b dynamic range using the switched-opf,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~32, no.~7, 1997.

\item
C.~K. Thanh, S.~H. Lewis, and P.~J. Hurst, ``A second-order double-sampled
  delta-sigma modulator using individual-lev el averaging,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~32, no.~8, 1997.

\item
E.~T. King, A.~Eshraghi, I.~Galton, and T.~S. Fiez, ``A nyquist-rate
  delta-sigma a/d converter,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~33,
  no.~1, 1998.

\item
A.~R. Feldman, B.~E. Boser, and P.~R. Gray, ``A 13-bit, 1.4-ms/s sigma-delta
  modulator for rf baseband channel applica tions,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~33, no.~10, 1998.

\item
M.~P. Flynn and B.~Sheahan, ``A 400-msample/s, 6-b cmos folding and
  interpolating adc,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~33, no.~12,
  1998.

\item
I.~Fujimori and T.~Sugimoto, ``A 1.5 v, 4.1 mw dual-channel audio delta~sigma
  d/a converter,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~33, no.~12,
  1998.

\item
J.~M. Ingino and B.~A. Wooley, ``A continuously calibrated 12-b, 10-ms/s, 3.3-v
  a/d converter,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~33, no.~12,
  1998.

\item
I.~E. Opris, L.~D. Lewicki, and B.~C. Wong, ``A single-ended 12-bit 20
  msample/s self-calibrating pipeline a/d convert er,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~33, no.~12, 1998.

\item
V.~Peluso, P.~Vancorenland, A.~M. Marques, M.~S.~J. Steyaert, , and W.~Sansen,
  ``A 900-mv low-power a/d converter with 77-db dynamic range,'' \emph{{IEEE}
  J. Solid-State Circuits}, vol.~33, no.~12, 1998.

\item
S.~Tsukamoto, W.~G. Schoﬁeld, and T.~Endo, ``A cmos 6-b, 400-msample/s adc
  with error correction,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~33,
  no.~12, 1998.

\item
A.~Yasuda, H.~Tanimoto, and T.~Iida, ``A third-order ~ modulator using
  second-order noise-shaping dynamic eleme nt matching,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~33, no.~12, 1998.

\item
A.~M. Marques, V.~Peluso, M.~S.~J. Steyaert, , and W.~Sansen, ``A 15-b
  resolution 2-mhz nyquist rate adc in a 1- m cmos technology,'' \emph{{IEEE}
  J. Solid-State Circuits}, vol.~33, no.~7, 1998.

\item
D.-Y. Chang and S.-H. Lee, ``Design techniques for a low-power low-cost cmos
  a/d converter,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~33, no.~8, 1998.

\item
C.~M. Hammerschmied and Q.~Huang, ``Design and implementation of an untrimmed
  mosfet-only 10-bit a/d convert er with 79-db thd,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~33, no.~8, 1998.

\item
G.~Nicollini, S.~Pernici, P.~Confalonieri, C.~Crippa, A.~Nagari, S.~Mariani,
  A.~Calloni, M.~Moioli, and C.~Dallavalle, ``A high-performance analog
  front-end 14-bit codec for 2.7-v digital cellu lar phones,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~33, no.~8, 1998.

\item
B.~P. Brandt and J.~Lutsky, ``A 75-mw, 10-b, 20-msps cmos subranging adc with
  9.5 effective bits at ny quist,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~34, no.~12, 1999.

\item
O.~E. Erdo˘gan, P.~J. Hurst, , and S.~H. Lewis, ``A 12-b
  digital-background-calibrated algorithmic adc with 90-db thd,'' \emph{{IEEE}
  J. Solid-State Circuits}, vol.~34, no.~12, 1999.

\item
G.~Hoogzaad and R.~Roovers, ``A 65-mw, 10-bit, 40-msample/s bicmos nyquist adc
  in 0.8 mm/sup 2/,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~34, no.~12,
  1999.

\item
A.~Namdar and B.~H. Leung, ``A 400-mhz, 12-bit, 18-mw, if digitizer with mixer
  inside a sigma-delta m odulator loop,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~34, no.~12, 1999.

\item
S.~A. Paul, H.-S. Lee, J.~Goodrich, T.~F. Alailima, and D.~D. Santiago, ``A
  nyquist-rate pipelined oversampling a/d converter,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~34, no.~12, 1999.

\item
H.~Tao and J.~M.~K. and, ``A 400-ms/s frequency translating bandpass
  sigma-delta modulator,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~34,
  no.~12, 1999.

\item
H.~van~der Ploeg and R.~Remmers, ``A 3.3-v, 10-b, 25-msample/s two-step adc in
  0.35-/spl mu/m cmos,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~34,
  no.~12, 1999.

\item
J.~A. E.~P. van Engelen, R.~J. van~de Plassche, E.~Stikvoort, and A.~G. Venes,
  ``A sixth-order continuous-time bandpass sigma-delta modulator for digital
  radio if,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~34, no.~12, 1999.

\item
L.~Louis, J.~Abcarius, and G.~W. Roberts, ``An eighth-order bandpass /spl
  delta//spl sigma/ modulator for a/d conver sion in digital radio,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~34, no.~4, 1999.

\item
A.~M. Abo and P.~R. Gray, ``A 1.5-v, 10-bit, 14.3-ms/s cmos pipeline
  analong-to-digital converter,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~34, no.~5, 1999.

\item
C.~F. Edwards, W.~Redman-White, M.~Bracey, B.~M. Tenbroek, A.~Member, M.~S.~L.
  Lee, and M.~J. Uren, ``A multibit /spl sigma//spl delta/ modulator in
  floating-body sos/soi cmo s for extreme radiation envionments,'' \emph{{IEEE}
  J. Solid-State Circuits}, vol.~34, no.~7, 1999.

\item
Y.~Geerts, A.~M. Marques, M.~S.~J. Steyaert, and W.~Sansen, ``A 3.3-v, 15-bit,
  delta-sigma adc with a signal bandwidth of 1.1 mhz for adsl applications,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~34, no.~7, 1999.

\item
D.~B. Kasha, W.~L. Lee, and A.~Thomsen, ``A 16-mw, 120-db linear
  switched-capacitor delta-sigma modulator with dyn amic biasing,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~34, no.~7, 1999.

\item
I.~Mehr and D.~Dalton, ``A 500-msample/s, 6-bit nyquist-rate adc for disk-drive
  read-channel appl ications,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~34,
  no.~7, 1999.

\item
K.~Nagaraj, F.~Chen, T.~Le, and T.~R. Viswanathan, ``Efficient 6-bit a/d
  converter using a 1-bit folding front end,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~34, no.~8, 1999.

\item
I.~Fujimori, L.~Longo, A.~Hairapetian, K.~Seiyama, S.~Kosic, J.~Cao, and S.-L.
  Chan, ``A 90-db snr 2.5-mhz output-rate adc using cascaded multibit
  delta-sigma modulation at 8x oversampling ratio,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~35, no.~12, 2000.

\item
Y.~Geerts, M.~S.~J. Steyaert, and W.~Sansen, ``A high-performance multibit /spl
  delta//spl sigma/ cmos adc,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~35,
  no.~12, 2000.

\item
C.~Moreland, F.~Murden, M.~Elliott, J.~Young, M.~Hensley, and R.~Stop, ``A
  14-bit 100-msample/s subranging adc,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~35, no.~12, 2000.

\item
M.-J. Choe, B.-S. Song, and K.~Bacrania, ``A 13-b 40-msamples/s cmos pipelined
  folding adc with background offset t rimming,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~35, no.~12, 2000.

\item
K.~Nagaraj, D.~A. Martin, M.~Wolfe, R.~Chattopadhyay, S.~Pavan, J.~Cancio, and
  T.~R. Viswanathan, ``A dual-mode 700-msamples/s 6-bit 200-msamples/s 7-bit
  a/d converter in a 0.25-/spl mu/m digital cmos,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~35, no.~12, 2000.

\item
H.~Pan, M.~Segami, M.~Choi, J.~Cao, and A.~A. Abidi, ``A 3.3-v 12-b 50-ms/s a/d
  converter in 0.6-/spl mu/m cmos with over 80-db sfdr,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~35, no.~12, 2000.

\item
A.~Tabatabaei and B.~A. Wooley, ``A two-path bandpass sigma-delta modulator
  with extended noise shaping,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~35, no.~12, 2000.

\item
E.~J. van~der Zwan, K.~Philips, and C.~A.~A. Bastiaansen, ``A 10.7-mhz
  if-to-baseband /spl sigma//spl delta/ a/d conversion system for am/fm radio
  receivers,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~35, no.~12, 2000.

\item
W.-S. Wey and Y.-C. Huang, ``A cmos delta-sigma true rms converter,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~35, no.~2, 2000.

\item
I.~E. Opris, B.~C. Wong, and S.~W. Chin, ``A pipeline a/d converter
  architecture with low dnl,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~35,
  no.~2, 2000.

\item
S.-I. Liu, C.-H. Kuo, R.-Y. Tsai, and J.~Wu, ``A double-sampling
  pseudo-two-path bandpass /spl delta//sigma/ modulator,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~35, no.~2, 2000.

\item
E.~Fogleman, I.~Galton, W.~Huff, and H.~Jensen, ``A 3.3-v single-poly cmos
  audio adc delta-sigma modulator with 98-db peak sinad and 105-db peak sfdr,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~35, no.~3, 2000.

\item
I.~Mehr and L.~Singer, ``A 55-mw, 10-bit, 40-msample/s nyquist-rate cmos adc,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~35, no.~3, 2000.

\item
Y.-T. Wang and B.~Razavi, ``An 8-bit 150-mhz cmos a/d converter,'' \emph{{IEEE}
  J. Solid-State Circuits}, vol.~35, no.~3, 2000.

\item
B.-S. Song, P.~L. Rakers, and S.~F. Gillig, ``A 1-v 6-b 50-msamples/s
  current-interpolating cmos adc,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~35, no.~4, 2000.

\item
L.~J. Breems, E.~J. van~der Zwan, and J.~H. Huijsing, ``A 1.8-mw cmos /spl
  sigma//spl delta/ modulator with integrated mixer for a/d conversion of if
  signal,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~35, no.~4, 2000.

\item
P.~C. Maulik, M.~S. Chadha, W.~L. Lee, and P.~J. Crawley, ``A 16-bit 250-khz
  delta-sigma modulator and decimation filter,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~35, no.~4, 2000.

\item
S.~Mortezapour and E.~K.~F. Lee, ``A 1-v, 8-bit successive approximation adc in
  standard cmos process,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~35,
  no.~4, 2000.

\item
A.~Nagari, A.~Mecchia, E.~Viani, S.~Pernici, P.~Confalonieri, and G.~Nicollini,
  ``A 2.7-v 11.8-mw baseband adc with 72-db dynamic range for gsm applicatio
  ns,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~35, no.~6, 2000.

\item
R.~Maurino and P.~Mole, ``A 200-mhz if 11-bit fourth-order bandpass /spl
  utri//spl sigma/ in sige,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~35,
  no.~7, 2000.

\item
J.~C. Morizio, M.~Hoke, T.~Kocak, C.~Geddie, C.~Hughes, J.~Perry,
  S.~Madhavapeddi, M.~H. Hood, G.~Lynch, H.~Kondoh, T.~Kumamoto, T.~Okuda,
  H.~Noda, M.~Ishiwaki, T.~Miki, and M.~Nakaya, ``14-bit 2.2-ms/s sigma-delta
  adc's,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~35, no.~7, 2000.

\item
M.-H. Liu and S.-I. Liu, ``An 8-bit 10 /s folding and interpolating adc using
  the continuous-time a uto-zero technique,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~36, no.~1, 2001.

\item
M.~Waltari and K.~A.~I. Halonen, ``1-v 9-bit pipelined switched-opamp adc,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~36, no.~1, 2001.

\item
C.-H. Kuo, S.-L. Chen, L.-A. Ho, and S.-I. Liu, ``Cmos oversampling /spl
  sigma/s/spl delta/ magnetic-to-digital converters,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~36, no.~10, 2001.

\item
J.~Ming and S.~H. Lewis, ``An 8-bit 80-msample/s pipelined analog-to-digital
  converter with backgro und calibration,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~36, no.~10, pp. 1489--1497, 2001.

\item
L.~J. Breems, E.~C. Dijkmans, and J.~H. Huijsing, ``A quadrature data-dependent
  dem algorithm to improve image rejection of a complex /spl simga//spl delta
  modulator,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~36, no.~12, 2001.

\item
T.~Burger and Q.~Huang, ``A 13.5-mw 185-msample/s /spl delta//spl sigma/
  modulator for umts/gsm du al-standard if reception,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~36, no.~12, 2001.

\item
M.~Choi and A.~A. Abidi, ``A 6-b 1.3-gsample/s a/d converter in 0.35-/spl mu/m
  cmos,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~36, no.~12, 2001.

\item
K.~Gulati and H.-S. Lee, ``A low-power reconfigurable analog-to-digital
  converter,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~36, no.~12, 2001.

\item
H.~van~der Ploeg, G.~Hoogzaad, H.~A.~H. Termeer, M.~Vertregt, and R.~L.~J.
  Roovers, ``A 2.5-v 12-b 54-msample/s 0.25-/spl mu/m cmos adc in 1-mm/sup 2/
  with mi xed-signal chopping and calibration,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~36, no.~12, 2001.

\item
K.~Vleugels, S.~Rabii, and B.~A. Wooley, ``A 2.5-v sigma-delta modulator for
  broadband communications applications,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~36, no.~12, 2001.

\item
W.~W. Yang, D.~Kelly, I.~Mehr, M.~T. Sayuk, and L.~Singer, ``A 3-v 340mw 14-b
  75-msample/s cmos adc with 85-db sfdr at nyquist input,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~36, no.~12, 2001.

\item
M.-J. Choe, B.-S. Song, and K.~Bacrania, ``An 8-b 100-msample/s cmos pipelined
  folding adc,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~36, no.~2, 2001.

\item
P.~Rombouts, W.~D. Wilde, and L.~Weyten, ``A 13.5-b 1.2-v micropower extended
  counting a/d converter,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~36,
  no.~2, 2001.

\item
D.~U. Thompson and B.~A. Wooley, ``A 15-b pipelined cmos floating-point a/d
  converter,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~36, no.~2, 2001.

\item
M.~Dessouky and A.~Kaiser, ``Very low-voltage digital-audio /spl delta//spl
  sigma/ modulator with 88- db dynamic range using local,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~36, no.~3, 2001.

\item
E.~Fogleman, J.~Welz, and I.~Galton, ``An audio adc delta-sigma modulator with
  100-db peak sinad and 102-db dr using a second-order mismatch-shaping dac,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~36, no.~3, 2001.

\item
R.~C. Taft and M.~R. Tursi, ``A 100-ms/s 8-b cmos subranging adc with sustained
  parametric performance from 3.8 v down to 2.2 v,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~36, no.~3, 2001.

\item
C.~B. Wang, ``A 20-bit 25-khz delta-sigma a/d converter utilizing a
  frequency-shaped c hopper stabilization schemer,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~36, no.~3, 2001.

\item
P.~Cusinato, D.~Tonietto, F.~Stefani, and A.~Baschirotto, ``A 3.3-v cmos
  10.7-mhz sixth-order bandpass /spl sigma//spl delta/ modula tor with 74-db
  dynamic range,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~36, no.~4, 2001.

\item
H.-S. Chen, B.-S. Song, and K.~Bacrania, ``A 14-b 20-msamples/s cmos pipelined
  adc,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~36, no.~6, 2001.

\item
G.~Promitzer, ``12-bit low-power fully differential switched capacitor
  noncalibrating su ccessive approximation adc with 1 ms/s,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~36, no.~7, 2001.

\item
L.~Sumanen, M.~Waltari, and K.~A.~I. Halonen, ``A 10-bit 200-ms/s cmos parallel
  pipeline a/d converter,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~36,
  no.~7, 2001.

\item
T.~Tille, J.~Sauerbrey, and D.~Schmitt-Landsiedel, ``A 1.8-v mosfet only /spl
  sigma//spl delta/ modulator using substrate bia sed depletion-mode mos
  capacitors in series compensation,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~36, no.~7, 2001.

\item
S.~Jaganathan, S.~Krishnan, D.~Mensa, T.~Mathew, Y.~Betser, Y.~Wei, D.~Scott,
  M.~Urteaga, and M.~Rodwell, ``An 18-ghz continuous-time \u2013
  analog\u2013digital converter implemented in inp-transferred substrate hbt
  technologyp,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~36, no.~9, 2001.

\item
O.~Oliaei, P.~Clément, and P.~Gorisse, ``A 5-mw sigma-delta modulator with
  84-db dynamic range for gsm/edge,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~37, no.~1, 2002.

\item
T.-H. Kuo, K.-D. Chen, and H.-R. Yeng, ``A wideband cmos sigma-delta modulator
  with incremental data weighted ave raging,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~37, no.~1, 2002.

\item
V.~S.~L. Cheung, H.~C. Luong, and W.-H. Ki, ``A 1-v 10.7-mhz switched-opamp
  bandpass /spl sigma//spl delta/ modulator using double-sampling
  finitee-gain-compensation technique,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~37, no.~10, 2002.

\item
J.~F. Bulzacchelli, H.-S. Lee, J.~A. Misewich, and M.~B. Ketchen,
  ``Superconducting bandpass 16 modulator with 2.23-ghz center frequency and
  42.6-ghz sampling rate,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~37,
  no.~12, 2002.

\item
S.~K. Gupta and V.~Fong, ``A 64-mhz clock-rate /spl sigma//spl delta/ adc with
  88-db sndr and - 105 -db im3 distortion at a 1.5-mhz signal frequency,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~37, no.~12, 2002.

\item
F.~Henkel, U.~Langmann, A.~Hanke, S.~Heinen, and E.~Wagner, ``A1-mhz-bandwidth
  second-order continuous-time quadrature bandpass sigma- delta modulator for
  low-if radio receivers,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~37,
  no.~12, 2002.

\item
S.~M. Jamal, D.~Fu, N.~C.-J. Chang, and P.~J.~H. and, ``A 10-b 120-msample/s
  time-interleaved analog-to-digital converter with d igital background
  calibration,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~37, no.~12, 2002.

\item
J.~H.-C. Lin and B.~Haroun, ``An embedded 0.8 v/480 uw 6b/22 mhz flash adc in
  0.13-um digital cmos process using a nonlinear double interpolation
  technique,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~37, no.~12, 2002.

\item
J.~Sauerbrey, T.~Tille, D.~Schmitt-Landsiedel, and R.~Thewes, ``A 0.7-v
  mosfet-only switched-opamp 61 modulator in standard digital cmos
  technology,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~37, no.~12, 2002.

\item
R.~Schreier, J.~Lloyd, L.~Singer, D.~Paterson, M.~Timko, M.~Hensley,
  G.~Patterson, A.~Member, K.~Behel, and J.~Zhou, ``A 10~300-mhz if-digitizing
  ic with 90-105-db dynamic range and 15-333-kh z bandwidth,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~37, no.~12, 2002.

\item
P.~C.~S. Scholtens and M.~Vertregt, ``A 6-b 1.6-gsample/s flash adc in 0.18-um
  cmos using averaging termination,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~37, no.~12, 2002.

\item
R.~H.~M. van Veldhoven, B.~J. Minnis, H.~A. Hegt, and A.~H.~M. van Roermund,
  ``A 3.3-mw /spl sigma//spl delta/ modulator for umts in 0.18-/spl mu/m cmo s
  with 70-db dynamic range in 2-mhz bandwidth,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~37, no.~12, 2002.

\item
O.~Bajdechi and J.~H. Huijsing, ``A 1.8-v /spl delta//spl sigma/ modulator
  interface for an electret micro phone with on-chip reference,'' \emph{{IEEE}
  J. Solid-State Circuits}, vol.~37, no.~3, 2002.

\item
C.~Donovan and M.~P. Flynn, ``A digital 6-bit adc in 0.25-/spl mu/m cmos,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~37, no.~3, 2002.

\item
J.~Grilo, I.~Galton, K.~Wang, R.~G. Montemayor, and A.~Member, ``A 12-mw adc
  delta-sigma modulator with 80 db of dynamic range integrated in a single-chip
  bluetooth,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~37, no.~3, 2002.

\item
I.~Mehr, P.~C. Maulik, and D.~Paterson, ``A 12-bit integrated analog front end
  for broadband wireline networks,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~37, no.~3, 2002.

\item
A.~Shabra and H.-S. Lee, ``Oversampled pipeline a/d converters with mismatch
  shaping,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~37, no.~5, 2002.

\item
S.-Y.~S. Chuang and T.~L. Sculley, ``A digitally self-calibrating 14-bit 10-mhz
  cmos pipelined a/d converter,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~37, no.~6, 2002.

\item
M.~Keskin, U.-K. Moon, and G.~C. Temes, ``A 1-v 10-mhz clock-rate 13-bit cmos
  /spl delta//spl sigma/ modulator usi ng unity-gain-reset opamps,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~37, no.~6, 2002.

\item
T.~Salo, S.~Lindfors, and K.~A.~I. Halonen, ``A 80-mhz bandpass 16 modulator
  for a 100-mhz if receiver,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~37,
  no.~6, 2002.

\item
T.~Ueno, A.~Yasuda, T.~Yamaji, and T.~Itakura, ``A fourth-order bandpass /spl
  delta/-/spl sigma/ modulator using second-o rder bandpass noise-shaping,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~37, no.~6, 2002.

\item
C.-S. Lin and B.-D. Liu, ``A new successive approximation architecture for
  low-power low-cost cmos a/d converter,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~38, no.~1, 2003.

\item
C.~B. Wang, S.~Ishizuka, and B.~Y. Liu, ``A 113-db dsd audio adc using a
  density-modulated dithering schem,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~38, no.~1, 2003.

\item
T.~Watanabe, T.~Mizuno, and Y.~Makino, ``An all-digital analog-to-digital
  converter with 12-uv/lsb using moving-average filtering,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~38, no.~1, 2003.

\item
P.~Rombouts, J.~D. Maeyer, and L.~Weyten, ``A 250-khz 94-db double-sampling
  /spl sigma//spl delta/ modulation a/d co nverter with a modified noise
  transfer function,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~38, no.~10,
  2003.

\item
B.-M. Min, P.~Kim, F.~W. Bowman, III, D.~M. Boisvert, and A.~J. Aude, ``A 69-mw
  10-bit 80-msample/s pipelined cmos adc,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~38, no.~12, 2003.

\item
B.~Murmann and B.~E. Boser, ``A 12-bit 75-ms/s pipelined adc using open-loop
  residue amplification,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~38,
  no.~12, 2003.

\item
L.~Y. Nathawad, R.~Urata, B.~A. Wooley, and D.~A.~B. Miller, ``A
  40-ghz-bandwidth, 4-bit, time-interleaved a/d converter using photoconductive
  sampling,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~38, no.~12, 2003.

\item
R.~H.~M. van Veldhoven, ``A triple-mode continuous-time /spl sigma//spl lambda/
  modulator with swi tched-capacitor feedback dac for a gsm-edge/cdma2000/umts
  receiver,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~38, no.~12, 2003.

\item
Y.~Yang, A.~Chokhawala, M.~Alexander, J.~Melanson, and D.~Hester, ``A 114-db
  68-mw chopper-stabilized stereo multibit audio adc in 5.62 mm/s up 2/,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~38, no.~12, 2003.

\item
A.~Zanchi, F.~Tsay, and I.~Papantonopoluos, ``Impact of capacitor dielectric
  relaxation on a 14-bit 70-ms/s pipeline a dc in 3-v bicmos,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~38, no.~12, 2003.

\item
D.~Miyazaki, S.~Kawahito, and M.~Furuta, ``A 10-b 30-ms/s low-power pipelined
  cmos a/d converter using a pseudodiff erential architecture,'' \emph{{IEEE}
  J. Solid-State Circuits}, vol.~38, no.~2, 2003.

\item
M.~R. Miller and C.~S. Petrie, ``A multibit sigma/delta adc for multimode
  receivers,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~38, no.~3, 2003.

\item
T.~O. Salo, S.~J. Lindfors, T.~M. Hollman, J.~A.~M. Järvinen, and K.~A.~I.
  Halonen, ``80-mhz bandpass /spl delta//spl sigma/ modulators for multimode
  digital if receivers,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~38,
  no.~3, 2003.

\item
K.~Uyttenhove, J.~Vandenbussche, E.~Lauwers, G.~G.~E. Gielen, and M.~S.~J.
  Steyaert, ``Design techniques and implementation of an 8-bit 200-ms/s
  interpolating/averaging cmos a/d converter,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~38, no.~3, 2003.

\item
E.~B. Blecker, T.~M. McDonald, O.~E. Erdo˘gan, P.~J. Hurst, , and S.~H. Lewis,
  ``Digital background calibration of an algorithmic analog-to-digital conve
  rter using a simplified queue,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~38, no.~6, 2003.

\item
C.~Davis and I.~Finvers, ``A 14-bit high-temperature sigma-delta modulator in
  standard cmos,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~38, no.~6, 2003.

\item
R.~Gaggl, A.~Wiesbauer, G.~Fritz, C.~Schranz, and P.~Pessl, ``A 85-db dynamic
  range multibit delta-sigma adc for adsl-co applications in 0.18-/spl mu/m
  cmos,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~38, no.~7, 2003.

\item
M.~S. Kappes, ``A 2.2-mw cmos bandpass continuous-time multibit 1–6 adc with
  68 db of dynamic range and 1-mhz bandwidth for wireless applications,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~38, no.~7, 2003.

\item
K.~Kaviani, Ömer Oralkan, P.~Khuri-Yakub, , and B.~A. Wooley, ``A multichannel
  pipeline analog-to-digital converter for an integrated 3-d ultrasound imaging
  system,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~38, no.~7, 2003.

\item
J.~Sauerbrey, D.~Schmitt-Landsiedel, and R.~Thewes, ``A 0.5-v 1 uw successive
  approximation adc,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~38, no.~7,
  2003.

\item
M.~D. Scott, B.~E. Boser, and K.~S.~J. Pister, ``An ultralow-energy adc for
  smart dust,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~38, no.~7, 2003.

\item
K.~Uyttenhove and M.~S.~J. Steyaert, ``A 1.8-v 6-bit 1.3-ghz flash adc in
  0.25-/spl mu/m cmos,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~38, no.~7,
  2003.

\item
D.-Y. Chang and U.-K. Moon, ``A 1.4-v 10-bit 25-ms/s pipelined adc using
  opamp-reset switching techniq ue,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~38, no.~8, 2003.

\item
F.~Gerfers, M.~Ortmanns, and Y.~Manoli, ``A 1.5-v 12-bit power-efficient
  continuous-time third-order /spl sigma//s pl delta/ modulator,'' \emph{{IEEE}
  J. Solid-State Circuits}, vol.~38, no.~8, 2003.

\item
Y.~Li and E.~Sánchez-Sinencio, ``A wide input bandwidth 7-bit 300-msample/s
  folding and current-mode interpolating adc,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~38, no.~8, 2003.

\item
M.~Inerfield, W.~Skones, S.~Nelson, D.~Ching, P.~Cheng, and C.~Wong, ``High
  dynamic range inp hbt delta-sigma analog-to-digital converters,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~38, no.~9, 2003.

\item
R.~Jiang and T.~S. Fiez, ``A 14-bit 16 adc with 8 osr and 4-mhz conversion
  bandwidth in a 0.18-um cmos process,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~39, no.~1, 2004.

\item
F.~Vessal and C.~A.~T. Salama, ``An 8-bit 2-gsample/s folding-interpolating
  analog-to-digital converter in sige technology,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~39, no.~1, 2004.

\item
S.~Yan and E.~Sánchez-Sinencio, ``A continuous-time 61 modulator with 88-db
  dynamic range and 1.1-mhz signal bandwidth,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~39, no.~1, 2004.

\item
A.~E. Cosand, J.~F. Jensen, H.~C. Choe, and C.~H. Fields, ``If-sampling
  fourth-order bandpass 16 modulator for digital receiver applications,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~39, no.~10, 2004.

\item
J.~Lee, P.~Roux, U.-V. Koc, T.~Link, Y.~Baeyens, and Y.-K. Chen, ``A 5-b
  10-gsample/s a/d converter for 10-gb/s optical receivers,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~39, no.~10, 2004.

\item
C.-H. Kuo and S.-I. Liu, ``A 1-v 10.7-mhz fourth-order bandpass 16 modulators
  using two switched opamps,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~39,
  no.~11, 2004.

\item
E.~H. Dagher, P.~A. Stubberud, W.~K. Masenten, L.~Member, M.~Conta, and T.~V.
  Dinh, ``A 2-ghz analog-to-digital delta-sigma modulator for cdma receivers
  with 79-db signal-to-noise ratio in 1.23-mhz bandwidth,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~39, no.~11, 2004.

\item
L.~Yao, M.~S.~J. Steyaert, and W.~Sansen, ``A 1-v 140-uw 88-db audio
  sigma-delta modulator in 90-nm cmos,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~39, no.~11, 2004.

\item
X.~Wang, P.~J. Hurst, and S.~H. Lewis, ``A 12-bit 20-msample/s pipelined
  analog-to-digital converter with nested digital background calibration,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~39, no.~11, 2004.

\item
B.~V. Amini and F.~Ayazi, ``A 2.5-v 14-bit 61 cmos soi capacitive
  accelerometer,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~39, no.~12,
  2004.

\item
P.~Balmelli and Q.~Huang, ``A 25-ms/s 14-b 200-mw 61 modulator in 0.18-um
  cmos,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~39, no.~12, 2004.

\item
L.~J. Breems, R.~Rutten, and G.~Wetzker, ``A cascaded continuous-time 61
  modulator with 67-db dynamic range in 10-mhz bandwidth,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~39, no.~12, 2004.

\item
J.~Mulder, C.~M. Ward, C.-H. Lin, D.~Kruse, J.~R. Westra, M.~Lugthart,
  E.~Arslan, R.~J. van~de Plassche, K.~Bult, and F.~M.~L. van~der Goes, ``A
  21-mw 8-b 125-msample/s adc in 0.09-mm2 0.13-um cmos,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~39, no.~12, 2004.

\item
K.~Philips, P.~A. C.~M. Nuijten, R.~L.~J. Roovers, A.~H.~M. van Roermund, F.~M.
  Chavero, M.~T. Pallarés, and A.~Torralba, ``A continuous-time 61 adc with
  increased immunity to interferers,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~39, no.~12, 2004.

\item
E.~Siragusa and I.~Galton, ``A digitally enhanced 1.8-v 15-bit 40-msample/s
  cmos pipelined adc,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~39, no.~12,
  pp. 2126--2138, 2004.

\item
R.~C. Taft, C.~A. Menkus, M.~R. Tursi, O.~Hidri, and V.~Pons, ``A 1.8-v
  1.6-gsample/s 8-b self-calibrating folding adc with 7.26 enob at nyquist
  frequency,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~39, no.~12, 2004.

\item
Y.~Chiu, P.~R. Gray, and B.~Nikolic´, ``A 14-b 12-ms/s cmos pipeline adc with
  over 100-db sfdr,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~39, no.~12,
  2004.

\item
J.-J. Sit and R.~Sarpeshkar, ``A micropower logarithmic a/d with offset and
  temperature compensation,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~39,
  no.~2, 2004.

\item
J.~D. Maeyer, P.~Rombouts, and L.~Weyten, ``A double-sampling extended-counting
  adc,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~39, no.~3, 2004.

\item
M.-H. Liu, K.-C. Huang, W.-Y. Ou, T.-Y. Su, and S.-I. Liu, ``A low
  voltage-power 13-bit 16 msps cmos pipelined adc,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~39, no.~5, 2004.

\item
T.~Zimmerman and J.~R. Hoff, ``The design of a charge-integrating modified
  floating-point adc chip,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~39,
  no.~6, 2004.

\item
A.~Gerosa, A.~Maniero, and A.~Neviani, ``A fully integrated two-channel a/d
  interface for the acquisition of cardiac signals in implantable pacemakers,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~39, no.~7, 2004.

\item
S.~Patón, A.~D. Giandomenico, L.~Hernández, A.~Wiesbauer, T.~Pötscher, and
  M.~Clara, ``A 70-mw 300-mhz cmos continuous-time 61 adc with 15-mhz bandwidth
  and 11 bits of resolution,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~39,
  no.~7, 2004.

\item
J.~Arias, V.~Boccuzzi, L.~Quintanilla, L.~Enríquez, D.~Bisbal, M.~Banu, and
  J.~Barbolla, ``Low-power pipeline adc for wireless lans,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~39, no.~8, 2004.

\item
V.~Colonna, G.~Gandolfi, F.~Stefani, and A.~Baschirotto, ``A 10.7-mhz
  self-calibrated switched-capacitor-based multibit second-order bandpass 61
  modulator with on-chip switched buffer,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~39, no.~8, 2004.

\item
J.-B. Park, S.-M. Yoo, S.-W. Kim, Y.-J. Cho, and S.-H. Lee, ``A 10-b
  150-msample/s 1.8-v 123-mw cmos a/d converter with 400-mhz input bandwidth,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~39, no.~8, 2004.

\item
J.~Li and U.-K. Moon, ``A 1.8-v 67-mw 10-bit 100-ms/s pipelined adc using
  time-shifted cds technique,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~39,
  no.~9, 2004.

\item
I.~Ahmed and D.~A. Johns, ``A 50-ms/s (35 mw) to 1-ks/s (15 uw) power scaleable
  10-bit pipelined adc using rapid power-on opamps and minimal bias current
  variation,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~40, no.~12, 2005.

\item
G.-C. Ahn, D.-Y. Chang, M.~E. Brown, N.~Ozaki, H.~Youra, K.~Yamamura,
  K.~Hamashita, K.~Takasuka, G.~C. Temes, and U.-K. Moon, ``A 0.6-v 82-db
  delta-sigma audio adc using switched-rc integrators,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~40, no.~12, 2005.

\item
L.~Dorrer, F.~Kuttner, P.~Greco, P.~Torta, and T.~Hartig, ``A 3-mw 74-db snr
  2-mhz continuous-time delta-sigma adc with a tracking adc quantizer in
  0.13-um cmos,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~40, no.~12, 2005.

\item
J.~McNeill, M.~C.~W. Coln, and B.~J. Larivee, ``Split adc architecture for
  deterministic digital background calibration of a 16-bit 1-ms/s adc,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~40, no.~12, 2005.

\item
K.~Nguyen, R.~Adams, K.~Sweetland, and H.~Chen, ``A 106-db snr hybrid
  oversampling analog-to-digital converter for digital audio,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~40, no.~12, 2005.

\item
J.~Yu and F.~Maloberti, ``A low-power multi-bit sigma-delta modulator in 90-nm
  digital cmos without dem,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~40,
  no.~12, 2005.

\item
Y.~L. Guillou, O.~Gaborieau, P.~Gamand, M.~Isberg, P.~Jakobsson, L.~Jonsson,
  D.~L. Daut, H.~Marie, S.~Mattisson, L.~Monge, T.~Olsson, S.~Prouet, and
  T.~Tired, ``Highly integrated direct conversion receiver for gsm/gprs/edge
  with on-chip 84-db dynamic range continuous-time delta sigma adc,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~40, no.~2, 2005.

\item
X.~Jiang and M.-C.~F. Chang, ``A 1-ghz signal bandwidth 6-bit cmos adc with
  power-efficient averaging,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~40,
  no.~2, 2005.

\item
J.~H. Shim, I.-C. Park, and B.~Kim, ``A third-order modulator in 0.18-m cmos
  with calibrated mixed-mode integrators,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~40, no.~4, 2005.

\item
J.~Li, G.-C. Ahn, D.-Y. Chang, and U.-K. Moon, ``A 0.9-v 12-mw 5-msps
  algorithmic with 77-db sfdri,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~40, no.~4, 2005.

\item
C.~R. Grace, P.~J. Hurst, and S.~H. Lewis, ``A 12-bit 80-msample/s pipelined
  adc with bootstrapped digital calibration,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~40, no.~5, 2005.

\item
S.~Limotyrakis, S.~D. Kulchycki, D.~K. Su, , and B.~A. Wooley, ``A 150-ms/s 8-b
  71-mw cmos time-interleaved adc,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~40, no.~5, 2005.

\item
H.-C. Liu, Z.-M. Lee, and J.-T. Wu, ``A 15-b 40-ms/s cmos pipelined
  analog-to-digital converter with digital background calibration,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~40, no.~5, 2005.

\item
A.~Zanchi and F.~C.-Y. Tsay, ``A 16-bit 65-ms/s 3.3-v pipeline adc core in sige
  bicmos with 78-db snr and 180-fs jitter,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~40, no.~6, 2005.

\item
T.~N. Andersen, B.~Hernes, A.~Briskemyr, F.~Telstø, J.~Bjørnsen, T.~E.
  Bonnerud, and Øystein Moldsvor, ``A cost-efficient high-speed 12-bit
  pipeline adc in 0.18-um digital cmos,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~40, no.~7, 2005.

\item
C.~Sandner, M.~Clara, A.~Santner, T.~Hartig, and F.~Kuttner, ``A 6-bit 1.2-gs/s
  low-power flash-adc in 0.13-um digital cmos,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~40, no.~7, 2005.

\item
Y.~Fujimoto, P.~L. Ré, and M.~Miyamoto, ``A delta-sigma modulator for a 1-bit
  digital switching amplifier,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~40, no.~8, 2005.

\item
K.~Nam, S.-M. Lee, D.~K. Su, , and B.~A. Wooley, ``A low-voltage low-power
  sigma-delta modulator for broadband analog-to-digital conversion,''
  \emph{{IEEE} J. Solid-State Circuits}, vol.~40, no.~8, 2005.

\item
V.~P. Petkov and B.~E. Boser, ``A fourth-order sigma-delta interface for
  micromachined inertial sensors,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~40, no.~8, 2005.

\item
H.~Y. Yang and R.~Sarpeshkar, ``A time-based energy-efﬁcient
  analog-to-digital converter,'' \emph{{IEEE} J. Solid-State Circuits},
  vol.~40, no.~8, 2005.

\item
T.~C. Caldwell and D.~A. Johns, ``A time-interleaved continuous-time 16
  modulator with 20-mhz signal bandwidth,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~41, no.~7, 2006.

\item
D.~Kurose, T.~Ito, T.~Ueno, T.~Yamaji, and T.~Itakura, ``55-mw 200-msps 10-bit
  pipeline adcs for wireless receivers,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~41, no.~7, 2006.

\item
S.-C. Lee, K.-D. Kim, J.-K. Kwon, J.~Kim, and S.-H. Lee, ``A 10-bit 400-ms/s
  160-mw 0.13-um cmos,'' \emph{{IEEE} J. Solid-State Circuits}, vol.~41, no.~7,
  2006.

\item
V.~Quiquempoix, P.~Deval, A.~Barreto, G.~Bellini, J.~Márkus, J.~Silva, and
  G.~C. Temes, ``A low-power 22-bit incremental adc,'' \emph{{IEEE} J.
  Solid-State Circuits}, vol.~41, no.~7, 2006.

\item
H.~van~der Ploeg, M.~Vertregt, and M.~Lammers, ``A 15-bit 30-ms/s 145-mw
  three-step adc for imaging applications,'' \emph{{IEEE} J. Solid-State
  Circuits}, vol.~41, no.~7, 2006.

%\end{description}
\end{enumerate}


%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../../wulff/work/ntnu/phd/thesis/thesis"
%%% End: 
